Beyond Ultra-Diffuse Galaxies I: Mass-Size Outliers Among the Satellites of Milky Way Analogs

### 2022-10-26 paper1.tex
right before submitting to arxiv

%% Reintroduced the \received and \accepted commands from AASTeX v5.2
\received{\today}
\revised{\today}
\accepted{\today}

@@

Our definition of UPG greatly benefits from the well-measured mass-size relation in \citet{ELVES-I} and the fact that this mass-size relation is independent of galaxy color and morphology. However, such mass-size relations are not always available for all galaxy mass ranges and environments (in the field or in groups and clusters). \citet{ELVES-I} derive the mass-size relation of satellite galaxies of MW analogs below $M_\star \sim 10^{8.5}\ M_\odot$, and find it similar to the mass-size relation of field late-type dwarfs in \citet{Karachentsev2013}. \citet{Lange2015} have relatively good constraints on the mass-size relation above $M_\star \sim 10^{9}\ M_\odot$. However, the mass-size relation at $10^{8.5}\ M_\odot < M_\star < 10^{9.5}\ M_\odot$ has been shown to be very shallow \citep{SmithCastelli2008,Misgeld2008,Misgeld2011,Eigenthaler2018}, and its dependence on color, morphology, or environment is still unclear. In this work, we simply extrapolate the \citet{ELVES-I} mass-size relation to $10^9\ M_\odot$. However, it is not clear whether the mass-size relation at $10^{8.5}\ M_\odot < M_\star < 10^{9}\ M_\odot$ is sensitive to color or morphology.

>>>>

%% Reintroduced the \received and \accepted commands from AASTeX v5.2
% \received{\today}
% \revised{\today}
% \accepted{\today}

@@

Our definition of UPG greatly benefits from the well-measured mass-size relation in \citet{ELVES-I} and the fact that this mass-size relation is independent of galaxy color and morphology. However, such mass-size relations are not always available for all galaxy mass ranges and environments (in the field or in groups and clusters). \citet{ELVES-I} derive the mass-size relation of satellite galaxies of MW analogs below $M_\star \sim 10^{8.5}\ M_\odot$, and find it similar to the mass-size relation of field late-type dwarfs in \citet{Karachentsev2013}. \citet{Lange2015} have relatively good constraints on the mass-size relation above $M_\star \sim 10^{9}\ M_\odot$. However, the mass-size relation at $10^{8.5}\ M_\odot < M_\star < 10^{9.5}\ M_\odot$ has been shown to be very shallow for red galaxies \citep{SmithCastelli2008,Misgeld2008,Misgeld2011,Eigenthaler2018}, and its dependence on color, morphology, or environment is still unclear. In this work, we simply extrapolate the \citet{ELVES-I} mass-size relation to $10^9\ M_\odot$. However, it is not clear whether the mass-size relation at $10^{8.5}\ M_\odot < M_\star < 10^{9}\ M_\odot$ is sensitive to color or morphology.
